IRMS Ramp Tests

### 2021-09-03 irms_ramp_testing/irms_ramp_testing.Rmd
ramp testing

---
title: "IRMS Ramp Tests"
author: "Tristan Caro"
date: "8/31/2021"
output: html_document
---

@@

>>>>

---
title: "IRMS Ramp Tests"
author: "Tristan Caro"
date: "Last knitted `r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document: 
    df_print: paged
    number_sections: yes
    toc: yes
    toc_float: true
    toc_depth: 3
    code_folding: show
editor_options:
  chunk_output_type: console
---

@@

```{r}
sfames %>%
  ggplot(aes(x = `Area 2 (Vs)`, y = resolution, color = ramp_cpm)) +
  geom_point() +
  geom_smooth(se = FALSE,
              method = "lm") +
  facet_wrap(~ramp_cpm) +
  theme_classic()
```
